% WORK EXPERIENCE ------------------------------------------------
\section{Work Experience}
  \CVSubHeadingListStart
%    \CVSubheading %Example
%      {What you did}{When you worked there}
%      {Who you worked for}{Where they are located}
%      \CVItemListStart
%        \CVItem{Why it is important to this employer}
%      \CVItemListEnd

  \CVSubheading
    {Birla Institute of Management Technology (BIMTECH)}{May 2025 -- \textit{Present}}
    {Assistant Professor - Economics and International Business}{Greater Noida, India}
    \CVItemListStart
      \CVItem{Delivering core and elective courses: Managerial Economics, Macroeconomics, Econometrics, Indian Economy, and Emerging Markets to PGDM/MBA students with a focus on managerial implications, applied learning and critical thinking.}
      \CVItem{Engage in research on development economics, migration, and financial inclusion and resilience with an aim of contributing to high-impact publications and academic conferences.}
      \CVItem{Contribute to administative roles including academic curriculum planning and strategic initiatives within the Economics and IB area.}
    \CVItemListEnd
  \CVSubheading
    {State Health Systems Resource Centre (SHSRC), Govt. of Meghalaya}{Dec. 2024 -- April 2025}
    {Senior Project Manager under UNICEF-IITB Project}{Shillong, India}
    \CVItemListStart
      \CVItem{Providing technical support for project management, research, impact evaluation, reporting, and reviewing health programs, as well as performance measurement in Meghalaya.}
      \CVItem{Conducting State Health Accounting in alignment with National Health Accounting standards to assess the status of healthcare financing in the state.}
      \CVItem{Identifying budget heads suitable for reallocation to Result-Based Financing initiatives for primary and secondary healthcare facilities in the state, aiming to enhance service delivery.}
      \CVItem{Develop comprehensive policy briefs for the state health administration and UNICEF, providing in-depth analysis and actionable recommendations to enhance health outcomes.}
    \CVItemListEnd
    
    \CVSubheading
      {CSR Study Unit, IIT Bombay}{July 2018 -- Feb. 2019}
      {Research Associate}{Mumbai, India}
      \CVItemListStart
        \CVItem{Research Area: Doable, replicable, and scalable Best CSR Practices in India}
        \CVItem{Consultation with Central Public Sector Enterprises (CPSEs) and IIT Bombay for collaborations in CSR projects.}
        \CVItem{Involved in high‑quality support with project management, research, proposal writing, impact evaluation, reporting, CSR program review and performance measurement, and annual review of CSR trends.}
        \CVItem{Organizing quarterly theme‑based CSR workshops for various CSR stakeholders including -- PSUs, NGOs and Government Organizations}     
      \CVItemListEnd
    \CVSubheading
      {Ministry of Rural Development (MoRD), Govt. of India}{July 2017 -- June 2018}
      {CTARA-IITB Research Fellow}{New Delhi, India}
      \CVItemListStart
        \CVItem{Research Area: Identifying technical bottlenecks of Direct Benefit Transfer (DBT) under National Social Assistance Program (NSAP)}
        \CVItem{Consultation with State Implementing Agencies and MoRD for understanding technical difficulties in implementing Public Finance Management System (PFMS) for efficient DBT to beneficiaries.}
        \CVItem{Involved with National Informatics Centre (NIC) of MoRD in designing work‑flow management system for pension disbursement (NSAP‑PPS).}
        \CVItem{Conducted National scheme workshops, participatory appraisal activities, Gap‑analysis, As‑in mapping, conceptualizing new process design for NSAP}     
      \CVItemListEnd
  \CVSubHeadingListEnd
