% HONORS AND AWARDS ------------------------------------------------
\section{Honors and Awards}
  \CVSubHeadingListStart
%    \CVSubheading % Example
%      {Work Presented}{When}
%      {Occasion}{Country}
    \CVSubheading
      {ADBI Funding for the 11th Conference on Asia and Pacific Economies}
      {May 2024 -- June 2024}
      {Conference Funding}
      {Sozhou, China}
      \CVItemListStart
      \CVItem{Received a full scholarship from the Asian Development Bank Institute (ADBI), Japan, to present research at the 11th Conference on Asia and Pacific Economies, held at Xi’an Jiaotong‑Liverpool University (XJTLU).}
      \CVItem{Paper titled ’Multidimensional Financial Resilience: An Ex‑ante Approach’ was selected for the special ADBI Session on Digitization and Resilience.}\      
      \CVItemListEnd

      \CVSubheading
      {J‑PAL/CLEAR Scholarship to Enrol in MITx Course}
      {Jan. 2023 -- Aug. 2023}
      {Scholarship}
      {Online}
      \CVItemListStart
      \CVItem{Awarded a \$1000 scholarship from J‑PAL/CLEAR South Asia to support enrolment in the MITx course on Designing and Running Randomized Evaluations.}
      \CVItem{Selection was based on an online examination, following the fulfillment of the minimum passing requirement.}     
      \CVItemListEnd

      \CVSubheading
      {UGC-NET in Economics}
      {Dec. -- 2022}
      {Qualification}
      {Online}
      \CVItemListStart
      \CVItem{Qualified UGC‑NET in Economics}     
      \CVItemListEnd

      \CVSubheading
      {Future Leader in Development, IIM Udaipur}
      {Dec. -- 2022}
      {Summer School}
      {Udaipur, India}
      \CVItemListStart
      \CVItem{Selected to participate in Summer School for Future Leaders in Development at IIM Udaipur in Collaboration with Sanford School of Public Policy, Duke University, USA.}
      \CVItem{Created business plan for the NGO Arth to encourage men to participate in Sexual and Reproductive Health programs in rural Rajasthan, India.}     
      \CVItemListEnd

      \CVSubheading
      {SDG Talent, UNLEASH Innovation Lab 2018, Singapore}
      {May 2018 -- June 2022}
      {Conference Funding}
      {Singapore}
      \CVItemListStart
      \CVItem{Selected to participate in the cohort of 1000 talents across the world to work on Sustainable Development Goals at Unleash Innovation Lab, held at National University of Singapore (NUS).}
      \CVItem{Employed Design Thinking tools to tackle the challenge of hidden hunger amongst adolescent girls in Urban Nepal.}     
      \CVItemListEnd

      \CVSubheading
      {Ministry of Rural Development Fellowship, IIT Bombay‑MoRD}
      {May 2018 -- June 2022}
      {Fellowship}
      {New Delhi}
      \CVItemListStart
      \CVItem{Awarded the CTARA-MoRD Joint Fellowship by the Ministry of Rural Development, Government of India, and IIT Bombay to conduct research on government social welfare programs.} 
      \CVItemListEnd
  
    \CVSubHeadingListEnd