%-----PUBLICATIONS ----------------------------------------------------
\section{Publications}
  \CVSubHeadingListStart
%    \CVSubheading
%      {Title of Work}{When it was done}
%      {Institution you worked with}{unused}
    \CVSubheading
      {Published Articles}{}
      {Research Articles}{}
      \CVItemListStart
        \CVItem{\textbf{Kamble P. A}, Mehta, A., Rani N. (2025). Measuring Multidimensional Financial Resilience: An Ex‑ante Approach, Social Indicators Research. 176, 533–567. DOI:\href{https://doi.org/10.1007/s11205-024-03476-8}{\color{blue}10.1007/s11205-024-03476-8}}\\ \vspace{2pt}
        \textbf{(Category: ABDC-A)} 
        \CVItem{\textbf{Kamble P. A}, Mehta, A., Rani N. (2024). Financial Inclusion and Digital Financial Literacy: Do they Matter for Financial Well-being? Social Indicators Research.171, 777–807. DOI:\href{https://doi.org/10.1007/s11205-023-03264-w}{\color{blue}10.1007/s11205-023-03264-w}}\\ \vspace{2pt}
        \textbf{(Category: ABDC-A)}
        \CVItem{M. P. Shah, \textbf{P. A. Kamble} and S. B. Agnihotri,Tackling child malnutrition: An innovative approach for training health workers using ICT a pilot study, 2016 IEEE Region 10 Humanitarian Technology Conference (R10-HTC), Agra, India, 2016, pp. 1- 6 DOI:\href{https://ieeexplore.ieee.org/abstract/document/7906811}{\space \color{blue}10.1109/R10-HTC.2016.7906811}} \\ \vspace{2pt}
        \textbf{(Category: Scopus)}    
      \CVItemListEnd

      \CVSubheading
      {Working Articles}{}
      {Research Articles}{}
      \CVItemListStart        
        \CVItem{Does financial literacy alleviate poverty? – New insights from a multidimensional approach  \textit{with Atul Mehta} submitted to \textit{World Development}. \textbf{(Category: ABDC-A)}}\\ \vspace{2pt}
        \CVItem{Socioeconomic Determinants of the Financial Inclusion Gender Gap in India: A Comparative Analysis of Access vs Usage Dimensions \textit{with Atul Mehta} submitted to \textit{Bulletin of Economic Research}. \textbf{(Category: ABDC-B)}}\\ \vspace{2pt}
        \CVItem{Household financial resilience and impact of shocks: Evidence from India}\\ \vspace{2pt}
        \CVItem{Household financial resilience and impact of idiosyncratic and covariate shocks}\\ \vspace{2pt}
        \CVItem{Determinants household financial resilience: a systematic literature review using ADO-TCM Framework}\\ \vspace{2pt}
      \CVItemListEnd
  \CVSubHeadingListEnd
