%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\cvsection{Awards and Honors}
%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\begin{cventries}
\cventry
{Funding for Conference} % Affiliation/role
{ADBI Funding for the 11th Conference on Asia and Pacific Economies} % Organization/group
{\textbf{Sozhou, China}} % Locationhttps://www.overleaf.com/project/62e7f2be7c9e6bf410fb1377
{May 2024 - June 2024} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Received a full scholarship from the Asian Development Bank Institute (ADBI), Japan, to present research at the 11th Conference on Asia and Pacific Economies, to be held at Xi’an Jiaotong‑Liverpool University (XJTLU), Suzhou, China}
\item {Paper titled 'Multidimensional Financial Resilience: An Ex‑ante Approach' was selected for the special ADBI Session on Digitization and Resilience.}
\end{cvitems}
}

\cventry
{Scholarship} % Affiliation/role
{Scholarship from J‑PAL/CLEAR to Enrol in MITx Course } % Organization/group
{\textbf{Online}} % Locationhttps://www.overleaf.com/project/62e7f2be7c9e6bf410fb1377
{Jan. 2023 - Aug. 2023} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Awarded a \$1000 scholarship from J‑PAL/CLEAR South Asia to support enrollment in the MITx course on Designing and Running Randomized Evaluations}
\item {Selection was based on an online examination, following the fulfillment of the minimum passing requirement.}
\end{cvitems}
}

\cventry
{Qualification} % Affiliation/role
{UGC-NET in Economics } % Organization/group
{\textbf{Online}} % Locationhttps://www.overleaf.com/project/62e7f2be7c9e6bf410fb1377
{Dec. 2022} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Qualified UGC-NET in Economics in 2022 among 28576 appeared candidates.}
\item {Qualified for Assistant Professor in Economics posts}
\end{cvitems}
}

\cventry
{Summer School} % Affiliation/role
{Future Leader in Development, IIM Udaipur} % Organization/group
{\textbf{Udaipur, India}} % Locationhttps://www.overleaf.com/project/62e7f2be7c9e6bf410fb1377
{June 2018 - July 2018} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Selected to participate in Summer School for Future Leaders in Development at IIM Udaipur in Collaboration with Sanford School of Public Policy, Duke University, USA.}
\item {Created business plan for the NGO \textit{Arth} to encourage men to participate in Sexual and Reproductive Health programs in rural Rajasthan, India.}
\end{cvitems}
}



%------------------------------------------------
\cventry
{Fully Funded} % Affiliation/role
{SDG Talent, UNLEASH Innovation Lab 2018 , Singapore} % Organization/group
{\textbf{Singapore}} % Location
{May 2018 - June 2018} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Selected to participate in the cohort of 1000 talents across the world to work on Sustainable Development Goals at Unleash Innovation Lab.}
\item {Employed Design Thinking tools to tackle the challenge of hidden hunger amongst adolescent girls in Urban Nepal.}
\end{cvitems}
}


%------------------------------------------------
\cventry
{Fully Funded} % Affiliation/role
{Ministry of Rural Development Fellowship, IIT Bombay- MoRD} % Organization/group
{\textbf{New Delhi, India}} % Location
{July 2017 - June 2018} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Awarded the CTARA MoRD fellowship by IIT Bombay to research on social welfare programs of Ministry of Rural Development, Government of India.}
\end{cvitems}
}


%------------------------------------------------

%------------------------------------------------
\end{cventries}